---
title: "Urbanization, energy consumption, and CO2 emissions with different income level countries"
author:
- familyname: Cui
  othernames: Di
  address: Monash University
  email: dcui0002@student.monash.edu
  correspondingauthor: true
  qualifications:  Master of Business Analytics
- familyname: Chen
  othernames: Guanru
  address: Monash University
  email: gche0054@student.monash.edu
  correspondingauthor: true
  qualifications: Master of Business Analytics
- familyname: Chen
  othernames: Yunzhi
  address: Monash University
  email: yche0537@student.monash.edu
  correspondingauthor: true
  qualifications:  Master of Business Analytics
department: TGIF \newline Di Cui &\newline Guanru Chen &\newline Yunzhi Chen
organization: World Bank
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
editor_options: 
  chunk_output_type: console
---

```{r , echo = FALSE, message = FALSE, warning = FALSE}
# Libraries

library(tidyverse)
library(readr)
library(kableExtra)
library(bookdown)
library(gridExtra)
library(viridis)
library(scales)
```

# Data set introduction



# Research questions



\clearpage

# Exploratory data analysis

\section*{}



\subsection*{Analysis} 


\clearpage

\section*{Brief about Meat Production}

- What's the status of meat production across the world?

- How did the CO2 emissions per capita of the two countries develop  from 1960 to 2020?

\subsection*{Research Question}

```{r load-data, echo = FALSE , message = FALSE, warning = FALSE}
GD <- read_csv(file = "Data/global-meat-production.csv")
MT <- read_csv(file = "Data/global-meat-production-by-livestock-type.csv")
```

## Q1
```{r production, echo = FALSE , message = FALSE, warning = FALSE}
production <- GD %>%
  select(-Code) %>% 
  filter(Entity %in% c("Asia",
                       "Europe",
                       "Northern America",
                       "South America",
                       "Central America",
                       "Africa",
                       "Oceania")) %>%
    rename("Production"= "Livestock Primary - Meat, Total - 1765 - Production - 5510 - tonnes") %>%
    group_by(Entity, Year)

plt_pd<- ggplot(production, aes(x= Year,
                                y= Production, 
                                fill= Entity)) + 
    geom_area(alpha=0.6 , size=.5, colour="white")+
    scale_fill_viridis(discrete = T) +
    theme_minimal()+
    ggtitle("Global meat production, 1961 to 2018")+
    scale_y_continuous(labels = comma_format(big.mark = "."))

ggplotly(plt_pd)
```

Regionally, **Asia is the largest meat producer**, accounting for near 50  percent of total meat production. This regional distribution has changed significantly in recent decades. In 1961, Europe and North America were the dominant meat producers, however Asia only produced little portion. By 2013, Europe and North America’s share had fallen noticeably.

```{r fig2, echo = FALSE , message = FALSE, warning = FALSE, fig.cap = "Comparison of the urbanization development"}
ET2 <- raw %>%
          dplyr::filter(Country_Name %in% c("Ethiopia",
                                            "Italy")) %>%
                 rename(Country = Country_Name) %>%
ggplot(aes(x = Year,
           y = Urban_population,
           fill = Country) ) +
  geom_bar(stat="identity", position=position_dodge()) +
  scale_fill_viridis_d(direction = 1) +
  theme_bw()

ET3 <- raw %>%
          dplyr::filter(IncomeGroup %in% c("Low income",
                                           "High income")) %>%
                 
ggplot(aes(x = Year,
           y = Urban_population,
           fill = IncomeGroup) ) +
  geom_bar(stat="identity", position=position_dodge()) +
  scale_fill_viridis_d(direction = -1) +
  theme_bw()

grid.arrange(ET2, ET3, nrow = 2)
```


In figure \@ref(fig:fig2) we observe the level of urbanization in Ethiopia is still strong, but on the other hand, Italy is quite stable. And we observe the similar trend in the plot of income group.

Based on this finding, we may conclude that the level of urbanization of the country may be significantly affected by its development of economic and its state income.

\clearpage

\section*{}


\subsection*{Analysis}



\clearpage

# Conclusion


\section*{Citation}
The data set is cited from @Worldbank.

Analysis of the data is done using the following packages:

bookdown @bookdown1, @bookdown2,

tidyverse @tidyverse,

readr @readr,

kableExtra @kableExtra.