---
title: "Urbanization, energy consumption, and CO2 emissions with different income level countries"
author:
- familyname: Cui
  othernames: Di
  address: Monash University
  email: dcui0002@student.monash.edu
  correspondingauthor: true
  qualifications:  Master of Business Analytics
- familyname: Chen
  othernames: Guanru
  address: Monash University
  email: gche0054@student.monash.edu
  correspondingauthor: true
  qualifications: Master of Business Analytics
- familyname: Chen
  othernames: Yunzhi
  address: Monash University
  email: yche0537@student.monash.edu
  correspondingauthor: true
  qualifications:  Master of Business Analytics
department: TGIF \newline Di Cui &\newline Guanru Chen &\newline Yunzhi Chen
organization: World Bank
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
---

```{r , echo = FALSE, message = FALSE, warning = FALSE}
# Libraries

library(tidyverse)
library(readr)
library(kableExtra)
library(bookdown)
library(gridExtra)
```

# Data set introduction



# Research questions



\clearpage

# Exploratory data analysis

\section*{}



\subsection*{Analysis} 


\clearpage

\section*{Country Ethiopia and Italy}

\subsection*{Exploratory data analysis}

```{r read-data2, echo = FALSE , message = FALSE, warning = FALSE}

raw <- read_csv(file = "Data/global-meat-production.csv")
```

```{r tab2, echo = FALSE , message = FALSE, warning = FALSE}
comparison <- raw %>%
  dplyr::filter(Country_Name %in% c("Ethiopia","Italy")) %>%
         group_by(Country_Name, Year) %>%
         rename(Country = Country_Name) %>% 
         summarize_at(vars(Urban_population), list(sum), na.rm = TRUE)

comparison_wide <- comparison %>% 
  pivot_wider(names_from = Country,
              values_from = Urban_population) %>% 
  filter(Year >= 1999)  
  
  
kable(comparison_wide, caption = "Urban population per year of Ethiopia and Italy from 1999-2018", booktabs = T) %>%
kable_material(c("striped", "hover"), position = "center")
```

Because the data is across over 40 years, which is a bit longer to present. So in Table \@ref(tab:tab2) we extract the urban population of two countries since 1999. And noticeably, the urban population of Ethiopia is lower than Italy throughout the whole period.

```{r fig2, echo = FALSE , message = FALSE, warning = FALSE, fig.cap = "Comparison of the urbanization development"}
ET2 <- raw %>%
          dplyr::filter(Country_Name %in% c("Ethiopia",
                                            "Italy")) %>%
                 rename(Country = Country_Name) %>%
ggplot(aes(x = Year,
           y = Urban_population,
           fill = Country) ) +
  geom_bar(stat="identity", position=position_dodge()) +
  scale_fill_viridis_d(direction = 1) +
  theme_bw()

ET3 <- raw %>%
          dplyr::filter(IncomeGroup %in% c("Low income",
                                           "High income")) %>%
                 
ggplot(aes(x = Year,
           y = Urban_population,
           fill = IncomeGroup) ) +
  geom_bar(stat="identity", position=position_dodge()) +
  scale_fill_viridis_d(direction = -1) +
  theme_bw()

grid.arrange(ET2, ET3, nrow = 2)
```


In figure \@ref(fig:fig2) we observe the level of urbanization in Ethiopia is still strong, but on the other hand, Italy is quite stable. And we observe the similar trend in the plot of income group.

Based on this finding, we may conclude that the level of urbanization of the country may be significantly affected by its development of economic and its state income.

\clearpage

\section*{}


\subsection*{Analysis}



\clearpage

# Conclusion


\section*{Citation}
The data set is cited from @Worldbank.

Analysis of the data is done using the following packages:

bookdown @bookdown1, @bookdown2,

tidyverse @tidyverse,

readr @readr,

kableExtra @kableExtra.